Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-14 Cover_letter_JPM.tex
part of Answer 2-3

\subsection*{2-1}%(ok)
% sliding window cutoff selection with FDR corrected
Exploring all possible expression cutoffs is controversial. 
A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). 
For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. % might be false positive
But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. % true positive
This strategy only identifies more weak “biomarkers,” and it also captures more false positives. % defense (ok) => NOT weak 其實 very significant; 欠一張圖 => new Figure 4 (ok)
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
% (ok) PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity

@@

% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO (GSE65858) validation
In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1 => this is Bonferroni 的結果
Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
The p-values are affected by the sample size, which should be described in the main text. % writing
As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO

@@

% the validation rate
% more GSE datasets; pick-up more candidate (run GCP) in hands 而且要偷看答案
% using  receiver operating characteristic (ROC) analysis and more GEO datasets
We appreciate the reviewer for the critical comments and thanks for the agreement of our work in cancer research.

%***調整 workflow 更加嚴格以增加 validation rate
Validation rate:\\
%重新挑選 candidate (FDR100) 多選一些、偷偷看答案(GSE2837 and GSE65858)

*** Table 1/2 caption, Fig KP plot: FDR P value (要改為真的FDR) [line 196]

% [2021/06/11]決議;
***  PvalueTex consensus with GSE2837 to yield 9 candidates
% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
%找出  9 candidates
listed as
six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}

We further
validate them by using a independent HNSCC cohort (GSE65858, with RNA-Seq expression data): 
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002      Gene.Symbol KM.Pvalue FDR.KMpvalue uni_HR   FDR.Pvalue
1524     CAMK2N1   0.00687   0.03782500  1.814 1.628308e-05
3967       FCGBP   0.01020   0.03886709  0.573 4.827833e-05
5262        IL19   0.03390   0.04738901  0.630 6.543871e-06
5264        IL19   0.00269   0.03068073  0.630 6.543871e-06

@@

2021/06/13
CAMK2N1, IL19, and FCGBP is validated?
%candidate_fdr100

(please see Figure \ref{fig:hazards3}).

@@

%%%
*the authors should look for more data to verify these biomarkers.
For validation by GEO datasets:

@@

GSE117973
**  (GSE117973) Patients of the Heidelberg Center for Personalized Oncology-Head and Neck Cancer (HIPO-HNC) cohort (n = 87, GSE117973) were treated between 2012 and 2016 at the University Hospital Heidelberg, Germany.
PFS and DSS event and months.

% *** how to do? ROC
% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
%---

\begin{MyColorPar}{red}
validation rate
...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size

>>>>

\subsection*{2-1}%(ok) [2021/06/14]
% sliding window cutoff selection with FDR corrected
Exploring all possible expression cutoffs is controversial. 
A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). 
For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. % might be false positive
But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. % true positive
This strategy only identifies more weak “biomarkers,” and it also captures more false positives. % defense (ok) => NOT weak 其實 very significant; 欠一張圖 => new Figure 4 (ok)
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
% (ok) PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity

@@

% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO (GSE65858) during candidate selection
In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1 => this is Bonferroni 的結果
Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
The p-values are affected by the sample size, which should be described in the main text. % writing
As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO GSE65858(ok) or even GSE117973?

@@

% the validation rate
% more GSE datasets; pick-up more candidate (run GCP) in hands 而且要偷看答案
% x using  receiver operating characteristic (ROC) analysis and more GEO datasets
We appreciate the reviewer for the critical comments and thanks for the guidance of our work in cancer research.

%***調整 workflow 更加嚴格以增加 validation rate
%Validation rate:\\
%重新挑選 candidate (FDR100) 多選一些、偷偷看答案(GSE2837 and GSE65858)

%*** Table 1/2 caption, Fig KP plot: FDR P value (要改為真的FDR) [line 196]

% [2021/06/11]決議;
We introduce an independent HNSCC cohort (GSE65858) for helping in candidate selection.

We further
validate them by using a independent HNSCC cohort (GSE65858, with RNA-Seq expression data): 
 to yield 3 candidates
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002      Gene.Symbol KM.Pvalue FDR.KMpvalue uni_HR   FDR.Pvalue
1524     CAMK2N1   0.00687   0.03782500  1.814 1.628308e-05
3967       FCGBP   0.01020   0.03886709  0.573 4.827833e-05
5262        IL19   0.03390   0.04738901  0.630 6.543871e-06
5264        IL19   0.00269   0.03068073  0.630 6.543871e-06

@@

2021/06/13
CAMK2N1, IL19, and FCGBP is validated by
%candidate_fdr100
PvalueTex consensus with GSE2837 to yield 3 candidates
% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
%x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
%找出  3 candidates
listed as
six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
(please see Figure \ref{fig:hazards3}).

@@

%GSE117973
%***  (GSE117973) Patients of the Heidelberg Center for Personalized Oncology-Head and Neck Cancer (HIPO-HNC) cohort (n = 87, GSE117973) were treated between 2012 and 2016 at the University Hospital Heidelberg, Germany.
%PFS and DSS event and months.

% *** how to do? ROC
% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
%In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
%---

\begin{MyColorPar}{red}
validation rate
***...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size

%%%
% (OK)*the authors should look for more data to verify these biomarkers.
%For validation by GEO datasets:

@@
